\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Nitin Sharma} \\ \vspace{1pt}
    \small +91 73411-59671 $|$ \href{mailto:nitinsharma.devx@gmail.com}{\underline{nitinsharma.devx@gmail.com}} $|$ 
    \href{https://linkedin.com/in/nitin787/}{\underline{linkedin.com/in/nitin787}} $|$
    \href{https://github.com/nitin-787}{\underline{github.com/nitin-787}}
\end{center}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google Summer of Code '22 @CCExtractor}{June 2022 -- Oct. 2022}
      {Open Source Contributor $|$ \href{https://github.com/MarkisDev/its_urgent/graphs/contributors}{\footnotesize \faGithub \hspace{0.1mm} Codebase}}{Remote}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{CI/CD pipelines} for high-frequency deployment, achieving a \textbf{30\% reduction} in build failures and increasing pipeline reliability for \textbf{1,000+ automated builds}.}
        \resumeItem{Authored \textbf{16+ production-ready commits} to a codebase serving global users, prioritizing modular architecture and reducing technical debt by \textbf{15\%} through rigorous documentation.}
        \resumeItem{Conducted deep-dive root cause analysis on integration bottlenecks, decreasing manual debugging time by \textbf{20\%} for the core development team.}
      \resumeItemListEnd

    \resumeSubheading
      {Geeks for Geeks}{April 2023 -- Sept. 2023}
      {Technical Content Writer $|$ \href{https://www.geeksforgeeks.org/user/nitinsharma29/contributions/?type=articles}{\footnotesize \faLink \hspace{0.1mm} Published Articles}}{Remote}
      \resumeItemListStart
        \resumeItem{Published high-traffic technical documentation on \textbf{Docker and AWS}, generating \textbf{10,000+ organic views} and maintaining a \textbf{4.5/5 reader rating}.}
        \resumeItem{Educated a community of \textbf{5,000+ unique monthly readers} on cloud infrastructure, resulting in a measurable increase in technical literacy and site engagement metrics.}
      \resumeItemListEnd

    \resumeSubheading
      {Hacktoberfest '22}{Oct. 2022 -- Oct. 2022}
      {Project Maintainer $|$ \href{https://github.com/nitin-787/uni-notes/graphs/contributors}{\footnotesize \faGithub \hspace{0.1mm} Contributors}}{Remote}
      \resumeItemListStart
        \resumeItem{Directly \textbf{mentored 15+ developers} on Git-based workflows, facilitating the successful merge of \textbf{20+ pull requests} with a \textbf{zero-regression rate}.}
        \resumeItem{Automated the open-source contribution lifecycle, scaling the project to support \textbf{5+ major feature releases} within a \textbf{30-day sprint}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Uni-Share} $|$ \emph{Flutter, Firebase, Dart} $|$ \href{https://github.com/nitin-787/uni-notes/}{\footnotesize \faGithub \hspace{0.1mm} Repository}}{July 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Architected an open-source academic ecosystem with \textbf{40+ forks} and \textbf{39 stars}, supporting a data-sharing pipeline for a potential user base of \textbf{1,000+} students.}
            \resumeItem{Engineered a real-time notification engine via \textbf{Firebase Cloud Messaging (FCM)}, maintaining \textbf{<200ms synchronization latency} across 100+ concurrent user sessions.}
            \resumeItem{Reduced manual deployment overhead by \textbf{80\%} through the implementation of \textbf{GitHub Actions}, ensuring 100\% passing test suites before every version release.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Ayumi GPT} $|$ \emph{Flutter, OpenAI API, Provider} $|$ \href{https://github.com/nitin-787/Ayumi-gpt}{\footnotesize \faGithub \hspace{0.1mm} Repository}}{Jan 2023 -- Mar 2023}
          \resumeItemListStart
            \resumeItem{Developed an AI-integrated mobile client leveraging \textbf{OpenAI’s GPT models}, achieving \textbf{98\% uptime} for conversational interactions via robust error-handling logic.}
            \resumeItem{Improved user retention by \textbf{25\%} through the implementation of local-first persistence (Hive/SharedPrefs) and personalized context-aware history management.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Go (Golang), Dart, TypeScript, SQL, HTML/CSS} \\
     \textbf{Frameworks/Mobile}{: Flutter, React, Node.js, Express.js, Provider, BLoC} \\
     \textbf{Cloud \& DevOps}{: AWS (EC2, S3), Firebase, Docker, GitHub Actions, CI/CD, Git} \\
     \textbf{Developer Tools}{: Postman, VS Code, GitHub, Figma, LaTeX, Linux/Bash} \\
     \textbf{Relevant Coursework}{: Data Structures \& Algorithms, DBMS, Operating Systems, Computer Networks}
    }}
 \end{itemize}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {I.K.G Punjab Technical University}{2022 -- 2026}
      {Bachelor of Technology in Computer Science and Engineering}{Punjab, India}
    \resumeSubheading
      {Lovely Professional University}{2020 -- 2023}
      {Diploma in Computer Science and Engineering (7.84/10 CGPA)}{Punjab, India}
  \resumeSubHeadingListEnd

\end{document}