\documentclass[]{deedy-resume-openfont}

\begin{document}

\namesection{Nitin}{Sharma}{ \urlstyle{same} 
\href{mailto:nitinsharma.devx@gmail.com}{\faEnvelope \hspace{0.2mm} nitinsharma.devx@gmail.com} | 
\href{https://github.com/nitin-787}{\faGithub \hspace{0.2mm} Github - nitin-787} | 
\href{https://www.linkedin.com/in/nitin787/} {\faLinkedin \hspace{0.2mm} LinkedIn - nitin787}
}


\section{Experience}
\runsubsection{Geeks for Geeks}
\vspace{0.4mm}
\hfill \daterange{Apr 2023 – Sep 2023} \\
\descript{Technical Content Writer}
\vspace{0.7mm}
\hfill \location{\href{https://www.geeksforgeeks.org/user/nitinsharma29/contributions/?type=articles}{{\faLink \hspace{0.1mm} {Link: Articles}}}}
\vspace{1.7mm}
\begin{tightemize}
	\item \textbf{Authored 3} technical articles on \textbf{Docker and AWS}, which received over \textbf{10000+} views and contributed to readers' understanding of cloud computing.
\end{tightemize}
\sectionsep

\runsubsection{Hacktoberfest '22}
\vspace{0.4mm} 
\hfill \daterange{Oct 1, 2022 – Oct 31 2022} \\
\descript{Project Maintainer}  
\vspace{0.7mm} 
\hfill \location{Remote} | \location{\href{https://github.com/nitin-787/uni-notes/graphs/contributors}{{\faGithub \hspace{0.1mm} {Github}}}}
\vspace{1.7mm}
\begin{tightemize}
	\item \textbf{Mentored 15 first-time contributors} during Hacktoberfest, providing guidance on submitting high-quality pull requests.
	\vspace{-1mm}
	\item \textbf{Led the open-source development process}, helping contributors understand best practices and contributing to \textbf{5+ successful PRs.}
	\vspace{-1mm}
	\item \textbf{Assisted in merging 20+ pull requests}, fostering collaboration and contributing to the project's growth.
\end{tightemize}
\sectionsep


\runsubsection{Google Summer of Code '22 @CCExtractor}
\vspace{0.4mm} 
\hfill \daterange{Jun 12, 2022 – Oct 19, 2022} \\
\descript{Contributor}  
\vspace{0.7mm} 
\hfill \location{Remote} | \location{\href{https://github.com/MarkisDev/its_urgent/graphs/contributors}{{\faGithub \hspace{0.1mm} {Github}}}}
\vspace{1.7mm}
\begin{tightemize}
    \item Led integration tasks in \textbf{GSoC'22 @CCExtractor}, enhancing the CI/CD pipeline to optimize deployment efficiency and reduce integration issues.
    \vspace{-1mm}
    \item Managed the \textbf{CI/CD pipeline}, reducing build failures by \textbf{30\%} and improving deployment reliability.
    \vspace{-1mm}
    \item Analyzed build logs and system behavior during CI workflows to identify root causes of failures.
    \vspace{-1mm}
    \item Enhanced project functionality by \textbf{contributing 16 well-documented commits}, focusing on modularity and maintainability.
\end{tightemize}
\sectionsep



\section{Projects}
\runsubsection{Uni-Share}
\descript{| Flutter, Firebase}
\hfill \location{\href{https://github.com/nitin-787/uni-notes/}{{\faGithub \hspace{0.1mm} {Github Repository}}}}
\vspace{1.7mm}
\begin{tightemize}
    \item \textbf{Developed the Uni-Share app prototype,} aiming to support \textbf{1000+ users} for sharing academic resources like notes, assignments.
    \vspace{-1.7mm}
    \item Designed \textbf{backend workflows using Firebase}, ensuring secure data flow, real-time sync, and reliable cloud performance.
    \vspace{-1.7mm}
    \item \textbf{Integrated Firebase} enabling real-time data syncing, robust database management, and seamless backend services.
\end{tightemize}
\sectionsep

\runsubsection{Ayumi GPT}
\descript{| Flutter, OpenAI}
\vspace{1.4mm}
\hfill \location{\href{https://github.com/nitin-787/Ayumi-gpt}{{\faGithub \hspace{0.1mm} {Github Repository}}}}
\begin{tightemize}
    \item \textbf{Developed Ayumi GPT,} a mobile app powered by OpenAI’s GPT model, enabling real-time, interactive conversations.    
    \vspace{-1.7mm}
    \item \textbf{Integrated Chat GPT API,} enhancing user interactions with responsive AI-driven replies.
    \vspace{-1.7mm}
	\item \textbf{Implemented key features,} like personalized chat histories and suggestions, increasing user engagement.
\end{tightemize}
\sectionsep

\sectionline
\section{Technical Skills}
\descript {Languages:\location{C, C++, Go-lang, Dart}} \\
\vspace{0.3mm}
\descript {Technologies:\location{Flutter, React, TypeScript, Node.js,
Firebase, Docker, Git}}\\
\vspace{0.3mm}
\descript{Tools:\location{Visual Studio Code, GitHub, Postman, Figma, LaTex}}\\
\vspace{0.3mm}
\sectionsep

\sectionline
\section{Education}
\runsubsection{I.K.G Punjab Technical University} 
\vspace{0.3mm}
\hfill \daterange{2023 - 2026 (Expected)} \\
\descript{Bachelor of Technology in Computer Science and Engineering}
\vspace{0.3mm}
\hfill \location{Hoshiarpur, Punjab} \\
\sectionsep

\runsubsection{Lovely Professional University}
\vspace{0.3mm}
\hfill \daterange{2020 - 2023 \textbar{} 7.84/10 CGPA} \\
\descript{Diploma in Computer Science and Engineering}
\vspace{0.3mm}
\hfill \location{Phagwara, Punjab}
\sectionsep


\end{document}
